Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-06 paper/paper.tex
misc changes

Function @f1@ and @f2@ mutually invoke each other, so the stack will alternately push
frames @f1@ and @f2@ onto the top of the current stack. However, no two existing stack
components are identical in the state space. One can decide the reachability of a state
through Dyck state graph \cite{earl2010pushdown, earl2012introspective}, but simply
caching the explored states (i.e. @seen@) would not always make the analyzer terminate.

@@

The function @choices@ takes two arguments: a set of elements of type @T@, and an initial cache.
The return type of @choices@ is @(T, Cache)@ with an annotation \verb|@cps[Ans]|, which
denotes that @choices@ will iteratively return an element of type @T@ from the collection
along with the latest cache once @f@ is invoked, but the final returned value of the
function is type @Ans@.
The function @f@ is the delimited continuation captured by the @shift@ operator (formed by the computation), and will be executed after the @choices@'s call-site.
Once the function @f@ (which is the function @k@ in @nd@) is invoked and returned,
it returns to its call site where @nd@ will be invoked on the remaining elements of the collection.
Now we can use this function to sequentialize expressions in the @let@ case:

>>>>

Function @f1@ and @f2@ mutually invoke each other, so the frames of @f1@ and @f@ will be
alternately pushed onto the top of the current stack. However, no two existing stack
components are identical in the state space. One can decide the reachability of a state
through Dyck state graph \cite{earl2010pushdown, earl2012introspective}, but simply
caching the explored states (i.e. @seen@) would not always make the analyzer terminate.

@@

The function @choices@ takes two arguments: a set of elements of type @T@, and an initial cache.
The return type of @choices@ is @(T, Cache)@ with an annotation \verb|@cps[Ans]|, which
denotes that @choices@ will iteratively return an element of type @T@ from the collection
along with the latest cache once @f@ is invoked, but the final returned value of the
function is type @Ans@.
The function @f@ is the delimited continuation captured by the @shift@ operator.
Whenever we call @choices@, the subsequent computations that will be executed after its call-site
constitute the delimited continuation @f@.
Once the function @f@ (which is the function @k@ in @nd@) is invoked and returned,
it returns to its call site where @nd@ will be invoked on the remaining elements of the collection.
Now we can use this function to sequentialize expressions in the @let@ case:
